\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in,right=0.6in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\definecolor{myblue}{RGB}{0, 102, 204}

\pagestyle{empty}

\titleformat{\section}{
  \vspace{-6pt}\bfseries\color{myblue}\uppercase
}{}{0em}{}[\titlerule \vspace{-6pt}]

\begin{document}

%==================== HEADER ====================
\begin{center}
    {\LARGE \textbf{\color{myblue}ShivaGanesh Varikuppala}} \\
    \vspace{4pt}
    \small
    +91-7569167646 \;|\;
    vsgvarikuppala@gmail.com \;|\;
    https://www.linkedin.com/in/shivaganesh-v \;|\;
    https://github.com/shiva676466
\end{center}

\vspace{-10pt}

%==================== CAREER OBJECTIVE ====================
\section*{Career Objective}
A passionate computer science student aspiring to pursue a Software Engineer role, with proficiency in C++, Java, and a strong grasp of data structures and algorithms. Skilled in development, delivering scalable and high-performance solutions. Strong problem-solving abilities and leadership skills, with a track record of building impactful projects.

%==================== EDUCATION ====================
\section*{Education}

\textbf{Bachelor of Engineering in Computer Science} \hfill (2025 -- Present) \\
Chandigarh University, Mohali, Punjab \hfill CGPA: 8.59 \\
Relevant Coursework: Data Structures, Algorithms, Operating Systems, DBMS, Computer Networks, Machine Learning, Cloud Computing

\vspace{4pt}

\textbf{Senior Secondary (CBSE)} \hfill (2022 -- 2023) \\
Kendriya Vidyalaya, Amritsar, Punjab \hfill Percentage: 92.8\%

\vspace{4pt}

\textbf{Secondary (CBSE)} \hfill (2020 -- 2021) \\
Kendriya Vidyalaya, Amritsar, Punjab \hfill Percentage: 90.4\%

%==================== PROJECTS ====================
\section*{Projects}

\textbf{Learning Path Generator – Personalized Roadmap System} \hfill (Month -- Month 2026) \\
\textit{Flask, MongoDB, Matplotlib, Python}
\begin{itemize}[leftmargin=*]
\item Developed a personalized learning platform that generates structured roadmaps based on user goals, skill level, and interests.
\item Designed backend using Flask and MongoDB to dynamically store user profiles and track learning progress.
\item Implemented recommendation logic to suggest optimized learning paths, improving user engagement and learning efficiency.
\item Integrated data visualization using Matplotlib to display progress insights and performance analytics.
\item Built scalable APIs to handle user input, roadmap generation, and real-time updates.
\end{itemize}

\textbf{Simplify Tasks – Academic Workflow Manager} \hfill (Jul -- Nov 2025) \\
\textit{Next.js, React.js, Firebase, CSS}
\begin{itemize}[leftmargin=*]
\item Built a task coordination platform improving workflow efficiency for students.
\item Centralized submissions replacing scattered WhatsApp communication.
\item Reduced missed deadlines and improved accountability.
\end{itemize}

%==================== TECHNICAL SKILLS ====================
\section*{Technical Skills}

\textbf{Languages:} C++, Java, Python, JavaScript \\
\textbf{Frameworks/Tools:} React.js, Node.js, Flask, Firebase, GitHub \\
\textbf{Databases:} MongoDB, Firebase \\
\textbf{Technologies:} API Development, Data Visualization

%==================== INTERPERSONAL SKILLS ====================
\section*{Interpersonal Skills}

Communication, Collaboration, Adaptability, Problem-Solving, Leadership

%==================== ACHIEVEMENTS ====================
\section*{Achievements}

\begin{itemize}[leftmargin=*]
\item Achieved Gold Medal and Top 1\% nationwide in NPTEL Cloud Computing
\item Secured Top 50 position in Intra-College Final Project Exhibition
\item Published research paper on Multimodal Data Transfer (2023)
\item Active member of technical and innovation communities
\end{itemize}

%==================== CERTIFICATIONS ====================
\section*{Certifications}

\begin{itemize}[leftmargin=*]
\item Introduction to Generative AI – Google
\item Introduction to Object-Oriented Programming in Java – LearnQuest
\item Foundations of Cloud Computing – NPTEL
\item Web Development in HTML5 and CSS3 – Coincent
\end{itemize}

%==================== HOBBIES ====================
\section*{Hobbies and Interests}

Playing Badminton, Tech Blogging, Content Creation

\end{document}